\section{References}

\begin{enumerate}

     \item \hypertarget{1}{Yan J, Wang C, Cheng W, Gao M, Zhou A. A retrospective of knowledge graphs. Frontiers of Computer Science. 2018; 12 (1): 55-74.}
    
    \item \hypertarget{2}{ Mayank M. A guide to the knowledge graphs . https://towardsdatascience.com/a-guide-to-the-knowledge-graphs-bfb5c40272f1 . Aug 2021}
        
    \item \hypertarget{3}{Ehrlinger L, Wöß W. Towards a Definition of Knowledge Graphs. SEMANTiCS (Posters, Demos, SuCCESS). 2016; 48 (1-4): 2.}
    
    \item \hypertarget{4}{Schrader B. What’s the Difference Between an
Ontology and a Knowledge Graph? https://enterprise-knowledge.com/whats-the-difference-between-an-ontology-and-a-knowledge-graph/}

% cited in bib
    \item \hypertarget{5}{Fensel D, Simsek U, Angele K, Huaman E, Kärle E, Panasiuk O, et al. Knowledge graphs. : Springer; 2020.}
    
     \item \hypertarget{6}{Cyganiak R, Hyland-Wood D, Lanthaler M. RDF 1.1 Concepts and Abstract Syntax. W3C Proposed Recommendation. 2014}

    \item \hypertarget{7}{Suignard, Michel. "Internationalized Resource Identifiers (IRIs)". tools.ietf.org. Retrieved 2018-06-09.}
 
    \item \hypertarget{8}{Berven A, Christensen OA, Moldeklev S, Opdahl AL, Villanger KJ. A knowledge-graph platform for newsrooms. Computers in Industry. 2020; 123 103321.}
 
    \item \hypertarget{9}{Al-Moslmi T, Ocaña MG, Opdahl AL, Veres C. Named entity extraction for knowledge graphs: A literature overview. IEEE Access. 2020; 8 32862-32881.}
    
    \item \hypertarget{10}{Mansouri A, Affendey LS, Mamat A. Named entity recognition approaches. International Journal of Computer Science and Network Security. 2008; 8 (2): 339-344.}
   
   \item \hypertarget{11}{Lašek I, Vojtáš P. Various approaches to text representation for named entity disambiguation. International Journal of Web Information Systems. 2013;}


    \item \hypertarget{12}{J. W. Reed, Y. Jiao, T. E. Potok, B. A. Klump, M. T. Elmore, A. R. Hurson. TF-ICF: A New Term Weighting Scheme for Clustering Dynamic Data Streams. - 2006 5th International Conference on Machine Learning and Applications (ICMLA'06), ; 2006. pp. 258-263. 10.1109/ICMLA.2006.50.}

     \item \hypertarget{13}{Jurafsky D, Martin JH. Sequence labeling for parts of speech and named entities. Speech and Language Processing. 2020; .}
     
     \item \hypertarget{14}{Hachey B, Radford W, Curran JR. Graph-based named entity linking with wikipedia. 2011; 1-2.}
     
    \item \hypertarget{15}{Fang W, Zhang J, Wang D, Chen Z, Li M. Entity disambiguation by knowledge and text jointly embedding. Proceedings of the 20th SIGNLL conference on computational natural language learning, ; 2016. pp. 260-269.}
     
    \item \hypertarget{16}{Bing Liu. Sentiment Analysis and Opinion Mining, Morgan \&
Claypool Publishers; May 2012. }

    \item \hypertarget{17}{Benamara F, Cesarano C, Picariello A, Reforgiato Recupero D, Subrahmanian V. Sentiment analysis: Adjectives and adverbs are better than adjectives alone. ICWSM. 2005. }
     
     \item \hypertarget{18}{M. Kanakaraj, R. M. R. Guddeti. NLP based sentiment analysis on Twitter data using ensemble classifiers. - 2015 3rd International Conference on Signal Processing, Communication and Networking (ICSCN), ; 2015. pp. 1-5. 10.1109/ICSCN.2015.7219856. }
    
    \item \hypertarget{19}{Bautin M, Vijayarenu L, Skiena S. International Sentiment Analysis for News and Blogs. Proceedings of the International AAAI Conference on Web and Social Media. 2021; 2 (1): 19-26. https://ojs.aaai.org/index.php/ICWSM/article/view/18606.}
     
     \item \hypertarget{20}{Balahur A, Steinberger R, Kabadjov M, Zavarella V, Van Der Goot E, Halkia M, et al. Sentiment analysis in the news. arXiv preprint arXiv:1309.6202. 2013; .}
     
     \item \hypertarget{21}{ Cambria E. An Introduction to Concept-Level Sentiment Analysis. ; 2013.}
     
     \item \hypertarget{22}{ Godbole N, Srinivasaiah M, Skiena S. Large-Scale Sentiment Analysis for News and Blogs. ; 2007.}
     
     \item \hypertarget{23}{ Hisano R, Sornette D, Mizuno T, Ohnishi T, Watanabe T. High Quality Topic Extraction from Business News Explains Abnormal Financial Market Volatility. PLOS ONE. 2013; 8 (6): e64846. https://doi.org/10.1371/journal.pone.0064846.}
     
     \item \hypertarget{24}{ Rinaldi A, Russo C, Tommasino C. A semantic approach for document classification using deep neural networks and multimedia knowledge graph. Expert Systems with Applications. 2020; 169 114320. 10.1016/j.eswa.2020.114320.}
    
    \item \hypertarget{25}{ Blei DM, Ng AY, Jordan MI. Latent dirichlet allocation. the Journal of machine Learning research. 2003; 3 993-1022.}
     
    \item \hypertarget{26}{Bullinaria JA. Self organizing maps: fundamentals. Introduction to Neural. 2004; 1-15.}

    \item \hypertarget{27}{ Van Hulle MM. SOM Algorithm. Self-organizing Maps. 2012; .}

     \item \hypertarget{28}{Andrienko N, Andrienko G, Fuchs G, Slingsby A, Turkay C, Wrobel S. Visual Analytics for Data Scientists. ; 2020.}
     
     \item \hypertarget{29}{Bhalla K. Three Principles of Good Visualization | CU Management [Internet]. CU Management. 2018 [cited 25 January 2022]. Available from: https://www.cumanagement.com/blogs/2018/11/05/three-principles-good-visualization}
     

     \item \hypertarget{30}{Reynolds C. The 12 Basic Principles Of Data Visualization [Internet]. Datafloq. 2017 [cited 25 January 2022]. Available from: https://datafloq.com/read/the-12-basic-principles-of-data-visualization/}
    
    \item \hypertarget{31}{Maslennikova E. ELMo Word Representations For News Protection. CLEF (Working Notes), ; 2019.}
    
    \item \hypertarget{32}{Smith NA. Contextual word representations: A contextual introduction. arXiv preprint arXiv:1902.06006. 2019;}
     
    \item \hypertarget{33}{Mikolov T, Chen K, Corrado G, Dean J. Efficient estimation of word representations in vector space. arXiv preprint arXiv:1301.3781. 2013;}
    
    \item \hypertarget{34}{Melamud O, Goldberger J, Dagan I. context2vec: Learning generic context embedding with bidirectional lstm. Proceedings of the 20th SIGNLL conference on computational natural language learning, ; 2016. pp. 51-61.}
    
    \item \hypertarget{35}{Wikidata:Licensing - Wikidata [Internet]. Wikidata.org. 2022 [cited 25 January 2022]. Available from: https://www.wikidata.org/wiki/Wikidata:Licensing}
    
    \item \hypertarget{36}{Exceptions to copyright: Research. Assets.publishing.service.gov.uk.2014. 
    Available from: https://assets.publishing.service.gov.uk/government/uploads/
    \linebreak
    system/uploads/attachment\_data/file/375954/Research.pdf}
    

    
\end{enumerate}